X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on a conventional source

### 2014-03-03 hedpc.tex
new author contributions

\section*{Author contributions}
T.T. and M.A. wrote the manuscript text and performed the experiments. All
authors reviewed the manuscript.
\end{document}

>>>>

\section*{Author contributions}
CD and MS conceived the edge-on illumination scheme for grating interferometry. TT, ZW and MA designed the first experiment. TT and MA performed the experiment and analyzed the data. TT and MA wrote the manuscript with contributions from all authors.
\end{document}
